---
title: "Forest Carbon Model"
author: "Lizzy Schattle, Rich Viebrock, & Haley Grant"
date: "5/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# packages
library(tidyverse)
library(deSolve)
library(sensitivity)
```

Instructions

1. Implement this model in R (as a differential equation)

```{r part 1. implement model}

source("R/dexcarbon_play.R")

```


2. Run the model for 300 years (using the ODE solver) starting with an initial forest size of 10 kg/C, and using the following parameters

 canopy closure threshold of 50 kgC 
 K = 250 kg C (carrying capacity) 
 r = 0.01 (exponential growth rate before before canopy closure)
 g = 2 kg/year (linear growth rate after canopy closure)

Graph the results

```{r part 2. run the model using ODE solver}

# set the parameters

T = 300
C = 10
c = 50
r = 0.01
K = 250
g = 2

pcompare = list(c=c, r=r, K=K, g=g)

dexcarbon_play(time = T, C = C, parms = pcompare)

growth_result = data.frame(time=seq(from=1,to=300))

carbon_result = ode(C, growth_result$time, dexcarbon_play, pcompare)
head(carbon_result)

```

3. Run a sobol sensitivity analysis that explores how the estimated maximum and mean forest size (e.g maximum and mean values of C over the 300 years) varies with the pre canopy closure growth rate (r) and post-canopy closure growth rate (g) and canopy closure threshold and carrying capacity(K)

Assume that they are all normally distributed with means as given above and standard deviation of 10% of mean value

Graph the results of the sensitivity analysis as a box plot of maximum forest size and a plot of the two sobol indices (S and T)

Submit R markdown with model implementation, graphs and sensitivity analysis and R file with your model


```{r part 3. sobel sensitivity analysis}

```

