---
title: "Forest Carbon Model"
author: "Lizzy Schattle, Rich Viebrock, & Haley Grant"
date: "5/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Instructions

1. Implement this model in R (as a differential equation)

2. Run the model for 300 years (using the ODE solver)  starting with an initial forest size of 10 kg/C, and using the following parameters

 canopy closure threshold of 50 kgC 
 K = 250 kg C (carrying capacity) 
 r = 0.01 (exponential growth rate before before canopy closure)
 g = 2 kg/year (linear growth rate after canopy closure)

Graph the results

3. Run a sobol sensitivity analysis that explores how the estimated maximum and mean forest size (e.g maximum and mean values of C over the 300 years) varies with the pre canopy closure growth rate (r) and post-canopy closure growth rate (g) and canopy closure threshold and carrying capacity(K)

Assume that they are all normally distributed with means as given above and standard deviation of 10% of mean value

Graph the results of the sensitivity analysis as a box plot of maximum forest size and a plot of the two sobol indices (S and T)

Submit R markdown with model implementation, graphs and sensitivity analysis and R file with your model

```{r}
# packages
library(tidyverse)
library(deSolve)
library(sensitivity)
```

```{r}
# start with sobel
source("../R/dexcarbon_play.R")

# knowing the initial carbon

Cinitial = 10

```

