---
title: "Forest Carbon Model"
author: "Lizzy Schattle, Rich Viebrock, Haley Grant, & Pat Byrne"
date: "5/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# packages
library(tidyverse)
library(deSolve)
library(sensitivity)
set.seed(42)
```

Instructions

1. Implement this model in R (as a differential equation)

```{r part 1. implement model}

source("R/dexcarbon_play.R")

```


2. Run the model for 300 years (using the ODE solver) starting with an initial forest size of 10 kg/C, and using the following parameters

 canopy closure threshold of 50 kgC 
 K = 250 kg C (carrying capacity) 
 r = 0.01 (exponential growth rate before before canopy closure)
 g = 2 kg/year (linear growth rate after canopy closure)

Graph the results

```{r part 2. run the model using ODE solver}

# set the parameters

T = 300
C = 10
cc = 50
r = 0.01
K = 250
g = 2

pcompare = list(cc=cc, r=r, K=K, g=g)

dexcarbon_play(time = T, C = C, parms = pcompare)

growth_result = data.frame(time=seq(from=1,to=300))

carbon_result = ode(C, growth_result$time, dexcarbon_play, pcompare)
head(carbon_result)

```

3. Run a sobol sensitivity analysis that explores how the estimated maximum and mean forest size (e.g maximum and mean values of C over the 300 years) varies with the pre canopy closure growth rate (r) and post-canopy closure growth rate (g) and canopy closure threshold and carrying capacity(K)

Assume that they are all normally distributed with means as given above and standard deviation of 10% of mean value

Graph the results of the sensitivity analysis as a box plot of maximum forest size and a plot of the two sobol indices (S and T)

Submit R markdown with model implementation, graphs and sensitivity analysis and R file with your model


```{r part 3. sobel sensitivity analysis}
Cinitial=10

# Sensitivity to pre canopy closure growth rate (r), post-canopy closure growth rate (g), canopy closure threshold (cc) and carrying capacity (K)

# Set the number of parameters
np=100

# First set of samples
r = rnorm(mean=0.01, sd=0.001, n=np)
g = rnorm(mean=2, sd=0.2, n = np)
cc = rnorm(mean=50, sd=5, n = np)
K = rnorm(mean=250, sd=25, n=np)

X1 = cbind.data.frame(r=r, g=g, cc=cc, K=K)

# Second set of samples
r = rnorm(mean=0.01, sd=0.001, n=np)
g = rnorm(mean=2, sd=0.2, n = np)
cc = rnorm(mean=50, sd=5, n = np)
K = rnorm(mean=250, sd=25, n=np)

X2 = cbind.data.frame(r=r, g=g, cc=cc, K=K)


# Create sobel object to get sets ofparameters for running the model
sens_C = soboljansen(model = NULL,X1, X2, nboot = 300)

# Check parameter sets 
head(sens_C$X)
```


```{r }
# First set of parameters - going to run with these first to check that we've correctly modified her in-class code
sens_C$X[1,]
```


```{r }
# Repeating in-class illustrative code to make sure stuff works

# Gets results for 300 years (evaluating every year)
simtimes = seq(from=1, to=300)
parms = list(r=sens_C$X$r[1], g=sens_C$X$g[1], cc=sens_C$X$cc[1], K=sens_C$X$K[1])
result = ode(y=Cinitial, times=simtimes, func=dexcarbon_play, parms=parms)
colnames(result)=c("time","C")
result = as.data.frame(result)
head(result)

# Graph looks good enough to me 
ggplot(result, aes(time, C))+geom_point()
```


```{r }
# Extract metrics of interest from illustrative example
# Maximum carbon - again, above K which is not allowed
maxC = max(result$C)
maxC

# Mean carbon
meanC = mean(result$C)
meanC


```


